---
title: "annual_data"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(inspectdf)
library(naniar)
```

This code joins annual outcome data with annual index data

```{r import}

dmed_tidy <- 
  read_rds("data/dmed_tidy.rds")

dmed <- 
  read_rds("data/dmed.rds")

annual_indices <-
  read_rds("data/annual_indices.rds")

########################
# Output:
hsi_data <-
   read_rds("data/hsi_data.rds")

```


# Installation counts by type and total  

```{r}
annual_indices %>% 
  count(site_name) %>% as.data.frame()

dmed_tidy %>% 
  dplyr::filter(!location %in% c("us", "overseas")) %>% 
  group_by(location, type) %>% 
  summarise(count = sum(count)) %>% 
  pivot_wider(names_from = "type", values_from = "count") %>% 
  mutate(total = `Ambulatory Data` + Hospitalizations + `Reportable Events`) %>% 
  arrange(desc(total))


dmed_tidy %>% 
  count(location)

dmed_tidy %>% 
  count(hsi)

```



```{r dmed_hsi}

# Prepare DMED dataframe: filter out "us" and "overseas" totals; recode names to match names in indices df; filter hsi-all; filter a single strata (gender)

dmed <-
  dmed_tidy %>% 
    filter(location %in% c("benning", "bragg", "campbell", "jackson",
                           "polk", "hood", "stewart", "leonardwood", 
                           "riley", "irwin", "bliss"),
           hsi == "all",
           strata == "gender",
           category == "Total") %>% 
    dplyr::select(-category, -strata, -hsi) %>% 
    dplyr::mutate(location = dplyr::recode(location, jackson = "Fort Jackson"),
           location = dplyr::recode(location, benning = "Fort Benning"),                 
           location = dplyr::recode(location, bragg = "Fort Bragg"),
           location = dplyr::recode(location, campbell = "Fort Campbell"),
           location = dplyr::recode(location, polk = "Fort Polk"),
           location = dplyr::recode(location, hood = "Fort Hood"),
           location = dplyr::recode(location, stewart = "Fort Stewart"),
           location = dplyr::recode(location, leonardwood = "Fort Leonard Wood"),
           location = dplyr::recode(location, riley = "Fort Riley"),
           location = dplyr::recode(location, irwin = "Fort Irwin"),
           location = dplyr::recode(location, bliss = "Fort Bliss"),
           location = as.character(location)) 


# write_rds(dmed, "data/dmed.rds")

```


```{r index_long}

index_long <- 
  annual_indices %>% 
    filter(site_name %in% c("Fort Jackson", "Fort Benning", "Fort Bragg","Fort Campbell", "Fort Polk",
                            "Fort Hood", "Fort Stewart", "Fort Leonard Wood", "Fort Riley", "Fort Irwin", "Fort Bliss")) %>%
      pivot_longer(-c(site_name, year), names_to = "index", values_to = "value") %>% 
      mutate(year = as.integer(year)) 

index_long

# write_rds(index_long, file = "data/index_long.rds")

```



```{r joined_hsi}

# Join to indices of heat; center and scale heat index value (pooled, for each index/type - pooled over all included locations and years)  

# Check missing values (year 2019 not complete)

index_long %>% 
    left_join(dmed, by = c("site_name" = "location", "year" = "year")) %>% 
  naniar::gg_miss_var(facet = year)


# Center and scale function: centers and scales a variable to mean 0 and standard deviation 1
  # https://stackoverflow.com/questions/35775696/trying-to-use-dplyr-to-group-by-and-apply-scale

scale_this <- function(x){
  (x - mean(x, na.rm = TRUE)) / sd(x, na.rm = TRUE)
}


  
joined_hsi <-
  index_long %>% 
    left_join(dmed, by = c("site_name" = "location", "year" = "year")) %>% 
      filter(year < 2019) %>%  
  ungroup() %>% 
  dplyr::group_by(index, type) %>% 
      mutate(value_scaled = scale_this(value),
             count_scaled = scale_this(count)) %>% 
  ungroup() 


joined_hsi

# write_rds(joined_hsi, file = "data/joined_hsi.rds")
```


## Restrict years, filter out Fort Irwin; set reference location

```{r hsi_data, message = FALSE}


hsi_data <-
  joined_hsi %>% 
    filter(!site_name %in% "Fort Irwin",
           !(type %in% "Hospitalizations" & year %in% 1990),
           !(type %in% "Ambulatory Data" & year %in% 1997)) %>% 
    mutate(site_name = factor(site_name, ordered = FALSE),
         index = factor(index, ordered = FALSE),
         type = factor(type, ordered = FALSE),
         site_name = relevel(site_name, ref = "Fort Bliss"))

# write_rds(hsi_data, file = "data/hsi_data.rds")

hsi_data

levels(hsi_data$site_name)

summary(hsi_data)

