---
title: "annual_data"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
```

This code imports and tidies data processed in the `heat_stress` project for datasets needed to recreate manuscript figures.


```{r import}

dmed_tidy <- 
  read_rds("data/dmed_tidy.rds")

```


# Installation counts by type and total  

```{r}
dmed_tidy %>% 
  dplyr::filter(!location %in% c("us", "overseas")) %>% 
  group_by(location, type) %>% 
  summarise(count = sum(count)) %>% 
  pivot_wider(names_from = "type", values_from = "count") %>% 
  mutate(total = `Ambulatory Data` + Hospitalizations + `Reportable Events`) %>% 
  arrange(desc(total))

```















```{r dmed_hsi}

# this chunk leaves out joining "all_icd" used to calculate burden

dmed_hsi <-
  dmed_tidy %>% 
    filter(location %in% c("benning", "bragg", "campbell", "jackson",
                           "polk", "hood", "stewart", "leonardwood", 
                           "riley", "irwin", "bliss"),
           hsi == "all",
           strata == "gender",
           category == "Total") %>% 
    dplyr::select(-category, -strata, -hsi) %>% 
    dplyr::mutate(location = dplyr::recode(location, jackson = "fort_jackson"),
           location = dplyr::recode(location, benning = "fort_benning_ga"),                 
           location = dplyr::recode(location, bragg = "fort_bragg"),
           location = dplyr::recode(location, campbell = "fort_campbell"),
           location = dplyr::recode(location, polk = "fort_polk"),
           location = dplyr::recode(location, hood = "fort_hood"),
           location = dplyr::recode(location, stewart = "fort_stewart"),
           location = dplyr::recode(location, leonardwood = "fort_leonard_wood"),
           location = dplyr::recode(location, riley = "fort_riley"),
           location = dplyr::recode(location, irwin = "ntc_and_fort_irwin"),
           location = dplyr::recode(location, bliss = "fort_bliss"),
           location = as.character(location)) 

#%>% 
#  left_join(all_icd, by = c("type", "year", "location")) %>% 
#  mutate(burden = count/count_overall,
#         burden_rate = rate/rate_overall,
#         bct = case_when(location %in% c("fort_benning_ga", "fort_jackson", "fort_leonard_wood") ~ 1,
#                         !location %in% c("fort_benning_ga", "fort_jackson", "fort_leonard_wood") ~ 0)) 

```


```{r index_long}

index_long <- 
  annual_tables_list %>% 
    filter(installation %in% c("fort_benning_ga", "fort_bragg", "fort_campbell", "fort_jackson",
                               "fort_polk", "fort_hood", "fort_stewart", "fort_leonard_wood", "fort_riley",
                               "ntc_and_fort_irwin", "fort_bliss")) %>% 
    unnest(data) %>% 
    pivot_longer(., cols = `1990`:`2019`, names_to = "year", values_to = "value") %>% 
    mutate(year = as.integer(year)) 

 write_rds(index_long, file = "data/index_long.rds")

```



```{r joined_hsi}

# Join to indices of heat; center and scale heat index value (pooled, for each index/type - pooled over all included locations and years)  
  
joined_hsi <-
  index_long %>% 
    left_join(dmed_hsi, by = c("installation" = "location", "year" = "year")) %>% 
      drop_na(count) %>% 
  ungroup() %>% 
  dplyr::group_by(index, type) %>% 
      mutate(value_scaled = scale(value, center = TRUE, scale = TRUE)) %>% 
  ungroup() %>% 
  na.omit()

joined_hsi

 write_rds(joined_hsi, file = "data/joined_hsi.rds")
```
Next: `joined_data` to `annual_summary.Rmd`
Modified code below:


Annual models from DMED data.

```{r hsi_data, message = FALSE}

# note: does not include canopy data

hsi_data <-
  joined_hsi %>% 
    filter(!installation %in% "ntc_and_fort_irwin",
           !(type %in% "Hospitalizations" & year %in% 1990),
           !(type %in% "Ambulatory Data" & year %in% 1997)) %>% 
    mutate(installation = factor(installation, ordered = FALSE),
         index = factor(index, ordered = FALSE),
         type = factor(type, ordered = FALSE),
         installation = relevel(installation, ref = "fort_bliss"))

 write_rds(hsi_data, file = "data/hsi_data.rds")

levels(hsi_data$installation)

summary(hsi_data)



