---
title: "models"
output:
  html_document:
    toc: true
    toc_float: true
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(readxl)
library(knitr)
library(kableExtra)
library(magick)
library(purrr)
library(furrr)
library(boot)
library(lme4)
library(ICC) 
library(dotwhisker)
library(broom)
library(car)
library(reshape2)
library(sjPlot)
library(readxl)
library(broom.mixed)
library(bbmle)
library(glmmTMB)
library(performance)
library(MASS)
library(mgcv)
library(grid)
library(gridExtra)
library(tableone)
library(corrr)
library(psych)
library(zoo)
library(patchwork) # install_github("thomasp85/patchwork")
library(vcd)
library(table1)

```

Annual models from DMED data and annual indices of heat and humidity from NLDAS-2

- load and prepare data
- create outcome-specific datasets
- negative binomial models (with and w/out year term), non-bootstrap
- 2-year block bootstraps (2k resamples, `basic` and `bca` CIs)
- 3-year block bootstraps (2k resamples)
- standard bootstrap (2k resamples)


## Load and prepare data
```{r load_datasets, message = FALSE}

hsi_data <-
  read_rds("data/hsi_data.rds")

summary(hsi_data)

```

### Outcome-specific datasets

```{r outcome_filtered}

ambulatory_data <-
  hsi_data %>%
      filter(type %in% "Ambulatory Data") %>% 
      dplyr::select(index, site_name, year, count, value, population) %>% 
      mutate(site_name = as.character(site_name))


hospitalization_data <-
  hsi_data %>%
      filter(type %in% "Hospitalizations") %>% 
      dplyr::select(index, site_name, year, count, value, population) %>% 
      mutate(site_name = as.character(site_name))


rme_data <-
  hsi_data %>%
      filter(type %in% "Reportable Events") %>% 
      dplyr::select(index, site_name, year, count, value, population) %>% 
      mutate(site_name = as.character(site_name))


```



## Base models 

```{r}

nb_fun = function(df) {
  df %>%
    MASS::glm.nb(count ~ value + site_name + offset(log(population)), data = .)
}


# With year term
nb_year_fun = function(df) {
  df %>%
    MASS::glm.nb(count ~ value + site_name + year + offset(log(population)), data = .)
}


amb_nb <-
  ambulatory_data %>% 
    nest(data = site_name:population) %>% 
    mutate(nb_mod = map(data, nb_fun),
           nb_tidy =   map(nb_mod, ~ broom::tidy(., conf.int = TRUE)),
           nb_year_mod = map(data, nb_year_fun),
           nb_year_tidy = map(nb_year_mod, ~ broom::tidy(., conf.int = TRUE)))


hosp_nb <-
  hospitalization_data %>% 
    nest(data = site_name:population) %>% 
    mutate(nb_mod = map(data, nb_fun),
           nb_tidy =   map(nb_mod, ~ broom::tidy(., conf.int = TRUE)),
           nb_year_mod = map(data, nb_year_fun),
           nb_year_tidy = map(nb_year_mod, ~ broom::tidy(., conf.int = TRUE)))

hosp_nb 


rme_nb <-
  rme_data %>% 
    nest(data = site_name:population) %>% 
    mutate(nb_mod = map(data, nb_fun),
           nb_tidy =   map(nb_mod, ~ broom::tidy(., conf.int = TRUE)),
           nb_year_mod = map(data, nb_year_fun),
           nb_year_tidy = map(nb_year_mod, ~ broom::tidy(., conf.int = TRUE)))


#write_rds(amb_nb, "data/amb_nb.rds")
#write_rds(hosp_nb, "data/hosp_nb.rds")
#write_rds(rme_nb, "data/rme_nb.rds")

```



## Bootstrap negative binomial models

Issue: control for long-term time trends; including `year` as a dummy time variable pulls variance also associated with changes in temperature/heat.

Approach: bootstrap model, selecting iterations of 2-3 year intervals to control for time trend.  
Execute resampling of dataset and calculation of your statistics on these samples.


## Random year blocks

### 2-year block limits (min and max year)
```{r random_blocks}


amb_min_yr <- min(as.numeric(
                 hsi_data %>% 
                  filter(type %in% "Ambulatory Data") %>% 
                  pull(year)))

amb_max_yr <- max(as.numeric(
                 hsi_data %>% 
                  filter(type %in% "Ambulatory Data") %>% 
                  pull(year)))

hosp_min_yr <- min(as.numeric(
                 hsi_data %>% 
                  filter(type %in% "Hospitalizations") %>% 
                  pull(year)))

hosp_max_yr <- max(as.numeric(
                 hsi_data %>% 
                  filter(type %in% "Hospitalizations") %>% 
                  pull(year)))


rme_min_yr <- min(as.numeric(
                 hsi_data %>% 
                  filter(type %in% "Reportable Events") %>% 
                  pull(year)))

rme_max_yr <- max(as.numeric(
                hsi_data %>% 
                  filter(type %in% "Reportable Events") %>% 
                  pull(year)))

```


### Bootstrap random two year blocks
Draw random blocks with replacement; stitch to original dataframe length

```{r amb_boot_2yr, eval = FALSE}

amb_index_2yr_fun <- function(outcome_data, i) {
  # Select random start year
  random_year <- replicate(10, sample(amb_min_yr:(amb_max_yr - 1), size = 1, replace = TRUE))
  random_years <- as.integer(c(random_year, random_year + 1))
  # select the observations to subset. 
  block_obs <- 
    random_years %>%
      map_dfr(~outcome_data %>% filter(year %in% .x))
  # run regression for given replicate, return estimated coefficients
  coefficients(MASS::glm.nb(count ~ value + site_name + offset(log(population)), data = block_obs))
}

# citation("MASS")

ptm <- proc.time()

amb_boot_2yr_block <-
  ambulatory_data %>% 
    nest(amb_data = site_name:population) %>% 
  mutate(boot = map(amb_data, ~ boot(., amb_index_2yr_fun, 2000)),
         tidy = map(boot, ~ broom::tidy(., conf.int = TRUE, conf.level = 0.95, conf.method = "basic")),
         tidy_bca = map(boot, ~ tidy(., conf.int = TRUE, conf.level = 0.95, conf.method = "bca")))

proc.time() - ptm



write_rds(amb_boot_2yr_block, path = "data/amb_boot_2yr_block.rds")


```


```{r hosp_boot_2yr, eval = FALSE}

hosp_index_2yr_fun <- function(outcome_data, i) {
  # Select random start year
  random_year <- replicate(13, sample(hosp_min_yr:(hosp_max_yr - 1), size = 1, replace = TRUE))
  random_years <- as.integer(c(random_year, random_year + 1))
  
  # select the observations to subset. 
  block_obs <- 
    random_years %>%
      map_dfr(~outcome_data %>% filter(year %in% .x))
  # run regression for given replicate, return estimated coefficients
  coefficients(MASS::glm.nb(count ~ value + site_name + offset(log(population)), data = block_obs))
}


ptm <- proc.time()

hosp_boot_2yr_block <-
  hospitalization_data %>% 
    nest(hosp_data = site_name:population) %>% 
  mutate(boot = map(hosp_data, ~ boot(., hosp_index_2yr_fun, 2000)),
         tidy = map(boot, ~ tidy(., conf.int = TRUE, conf.level = 0.95, conf.method = "basic")))

proc.time() - ptm


write_rds(hosp_boot_2yr_block, path = "data/hosp_boot_2yr_block.rds")

```

Error in `mutate()`:
! Problem while computing `tidy_bca = map(boot, ~tidy(.,
  conf.int = TRUE, conf.level = 0.95, conf.method = "bca"))`.
Caused by error in `bca.ci()`:
! estimated adjustment 'w' is infinite


```{r  rme_boot_2yr, eval = FALSE}

rme_index_2yr_fun <- function(outcome_data, i) {
  # Select random start year
  random_year <- replicate(11, sample(rme_min_yr:(rme_max_yr - 1), size = 1, replace = TRUE))
  random_years <- as.integer(c(random_year, random_year + 1))
  
  # select the observations to subset. 
  block_obs <- 
     random_years %>%
      map_dfr(~outcome_data %>% filter(year %in% .x))
  # run regression for given replicate, return estimated coefficients
  coefficients(MASS::glm.nb(count ~ value + site_name + offset(log(population)), data = block_obs))
}


ptm <- proc.time()

rme_boot_2yr_block <-
  rme_data %>% 
    nest(re_data = site_name:population) %>% 
  mutate(boot = map(re_data, ~ boot(., rme_index_2yr_fun, 2000)),
         tidy = map(boot, ~ tidy(., conf.int = TRUE, conf.level = 0.95, conf.method = "basic")),
         tidy_bca = map(boot, ~ tidy(., conf.int = TRUE, conf.level = 0.95, conf.method = "bca")))
        
proc.time() - ptm



  
write_rds(rme_boot_2yr_block, path = "data/rme_boot_2yr_block.rds")


rme_boot_2yr_block %>% 
  pull(boot)

```








## Bootstrap 3 year blocks


```{r amb_boot_3yr}

# 20 year timeframe (1998-2018: stitch 6 replicates of 3 year blocks

amb_index_3yr_fun <- function(outcome_data, i) {
  # Select random start year
  random_year <- replicate(6, sample(amb_min_yr:(amb_max_yr - 2), size = 1, replace = TRUE))
  random_years <- as.integer(c(random_year, random_year + 1))
  # select the observations to subset. 
   block_obs <- 
      random_years %>%
        map_dfr(~outcome_data %>% filter(year %in% .x))
  # run regression for given replicate, return estimated coefficients
  coefficients(MASS::glm.nb(count ~ value + site_name + offset(log(population)), data = block_obs))
}


ptm <- proc.time()


amb_boot_3yr_block <-
  ambulatory_data %>%
    filter(index %in% c("mean_tmp", "mean_hi", "mean_wbgt")) %>% 
    nest(amb_data = site_name:population) %>% 
    mutate(boot = map(amb_data, ~ boot(., amb_index_3yr_fun, 2000)),
           tidy = map(boot, ~ tidy(., conf.int = TRUE, conf.level = 0.95, conf.method = "basic")))

proc.time() - ptm

write_rds(amb_boot_3yr_block, path = "data/amb_boot_3yr_block.rds")

```



```{r hosp_boot_3yr, eval = FALSE}

hosp_index_3yr_fun <- function(outcome_data, i) {
  # Select random start year
  random_year <- replicate(9, sample(hosp_min_yr:(hosp_max_yr - 2), size = 1, replace = TRUE))
  random_years <- as.integer(c(random_year, random_year + 1))
  # select the observations to subset. 
   block_obs <- 
        random_years %>%
          map_dfr(~outcome_data %>% filter(year %in% .x))
  # run regression for given replicate, return estimated coefficients
  coefficients(MASS::glm.nb(count ~ value + site_name + offset(log(population)), data = block_obs))
}


ptm <- proc.time()

hosp_boot_3yr_block <-
  hospitalization_data %>%
   filter(index %in% c("mean_tmp", "mean_hi", "mean_wbgt")) %>% 
    nest(hosp_data = site_name:population) %>% 
    mutate(boot = map(hosp_data, ~ boot(., hosp_index_3yr_fun, 2000)))

proc.time() - ptm



hosp_boot_3yr_block <-
  hosp_boot_3yr_block %>% 
    mutate(tidy = map(boot, ~ tidy(., conf.int = TRUE, conf.level = 0.95, conf.method = "basic")))


write_rds(hosp_boot_3yr_block, path = "data/hosp_boot_3yr_block.rds")


```

```{r  rme_boot_3yr, eval = FALSE}

rme_index_3yr_fun <- function(outcome_data, i) {
  # Select random start year
  random_year <- replicate(7, sample(rme_min_yr:(rme_max_yr - 2), size = 1, replace = TRUE))
  random_years <- as.integer(c(random_year, random_year + 1))
  # select the observations to subset. 
  block_obs <- 
      random_years %>%
        map_dfr(~outcome_data %>% filter(year %in% .x))
  # run regression for given replicate, return estimated coefficients
  coefficients(MASS::glm.nb(count ~ value + site_name + offset(log(population)), data = block_obs))
}


ptm <- proc.time()

rme_boot_3yr_block <-
  rme_data %>% 
   filter(index %in% c("mean_tmp", "mean_hi", "mean_wbgt")) %>% 
    nest(re_data = site_name:population) %>% 
    mutate(boot = map(re_data, ~ boot(., rme_index_3yr_fun, 2000)))

rme_boot_3yr_block <-
  rme_boot_3yr_block %>% 
    mutate(tidy = map(boot, ~ tidy(., conf.int = TRUE, conf.level = 0.95, conf.method = "basic")))

proc.time() - ptm

write_rds(rme_boot_3yr_block, path = "data/rme_boot_3yr_block.rds")



```


## Bootstrap - original (draw single observations)

```{r boot_single, eval = FALSE}

std_boot <- function(D, d){
	E = D[d,]
	return(coefficients(MASS::glm.nb(count ~ value + site_name + offset(log(population)), data = E)))
	
}

amb_boot_std <-
  ambulatory_data %>%
    nest(amb_data = site_name:population) %>%
    filter(index %in% c("mean_tmp", "mean_hi", "mean_wbgt")) %>% 
    mutate(std_boot = map(amb_data, ~ boot(., std_boot, R = 2000)),          
           tidy = map(std_boot, ~ tidy(., conf.int = TRUE, conf.level = 0.95, conf.method = "basic")))


hosp_boot_std <-
  hospitalization_data %>%
  filter(index %in% c("mean_tmp", "mean_hi", "mean_wbgt")) %>% 
    nest(hosp_data = site_name:population) %>% 
        mutate(std_boot = map(hosp_data, ~ boot(., std_boot, R = 2000)),          
               tidy = map(std_boot, ~ tidy(., conf.int = TRUE, conf.level = 0.95, conf.method = "basic")))


rme_boot_std <-
  rme_data %>%
    nest(rme_data = site_name:population) %>%
    filter(index %in% c("mean_tmp", "mean_hi", "mean_wbgt")) %>% 
    mutate(std_boot = map(rme_data, ~ boot(., std_boot, R = 2000)),          
           tidy = map(std_boot, ~ tidy(., conf.int = TRUE, conf.level = 0.95, conf.method = "basic")))


write_rds(amb_boot_std, path = "data/amb_boot_std.rds")
write_rds(hosp_boot_std, path = "data/hosp_boot_std.rds")
write_rds(rme_boot_std, path = "data/rme_boot_std.rds")

```

