---
title: "model_assess"
output:
  html_document:
    toc: true
    toc_float: true
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(readxl)
library(knitr)
library(kableExtra)
library(magick)
library(purrr)
library(furrr)
library(boot)
library(lme4)
library(ICC) 
library(dotwhisker)
library(broom)
library(car)
library(reshape2)
library(sjPlot)
library(readxl)
library(broom.mixed)
library(bbmle)
library(glmmTMB)
library(performance)
library(MASS)
library(mgcv)
library(grid)
library(gridExtra)
library(tableone)
library(corrr)
library(psych)
library(zoo)
library(patchwork) # install_github("thomasp85/patchwork")
library(vcd)
library(table1)

```

#Model Tables and Figures


## Load data
```{r load_datasets, message = FALSE}

hsi_data <-
  read_rds("data/hsi_data.rds")

summary(hsi_data)

## Models

amb_nb <-
  read_rds("data/amb_nb.rds") 

hosp_nb <-
  read_rds("data/hosp_nb.rds") 

rme_nb <-
  read_rds("data/rme_nb.rds") 

amb_boot_2yr_block <-
  read_rds("data/amb_boot_2yr_block.rds") 

hosp_boot_2yr_block <-
  read_rds("data/hosp_boot_2yr_block.rds") 

rme_boot_2yr_block <-
  read_rds("data/rme_boot_2yr_block.rds") 

amb_boot_3yr_block <-
  read_rds("data/amb_boot_3yr_block.rds") 


hosp_boot_3yr_block <-
  read_rds("data/hosp_boot_3yr_block.rds") 

rme_boot_3yr_block <-
  read_rds("data/rme_boot_3yr_block.rds") 

amb_boot_std <-
  read_rds("data/amb_boot_std.rds") 

hosp_boot_std <-
  read_rds("data/hosp_boot_std.rds") 

rme_boot_std <-
  read_rds("data/rme_boot_std.rds") 



```


## Model data transform - long

```{r }

## Combined panel RR plot

amb_boot2_long <-
  amb_boot_2yr_block %>%
    unnest(tidy) %>% 
    filter(term %in% "value") %>% 
    dplyr::select(index, statistic, bias, conf.low, conf.high) %>% 
    pivot_longer(cols = -index,
                 names_to = "term",
                 values_to = "value") %>% 
    mutate(outcome = "Ambulatory")
  
  
hosp_boot2_long <-
  hosp_boot_2yr_block %>%
    unnest(tidy) %>% 
    filter(term %in% "value") %>% 
    dplyr::select(index, statistic, bias, conf.low, conf.high) %>% 
    pivot_longer(cols = -index,
                 names_to = "term",
                 values_to = "value") %>% 
    mutate(outcome = "Hospitalizations")  


rme_boot2_long <-
  rme_boot_2yr_block %>%
    unnest(tidy) %>% 
    filter(term %in% "value") %>% 
    dplyr::select(index, statistic, bias, conf.low, conf.high) %>% 
    pivot_longer(cols = -index,
                 names_to = "term",
                 values_to = "value") %>% 
    mutate(outcome = "Reportable Events")  


# Join dataframes

boot2_long <-
  amb_boot2_long %>% 
    bind_rows(hosp_boot2_long) %>% 
    bind_rows(rme_boot2_long)

# write_rds(boot2_long, file = "data/boot2_long.rds")

boot2_long <-
  read_rds(path = "data/boot2_long.rds")
```





## IRR of two-year block bootstrap negative binomial models (Figure 2)
Select indices, 10,000 bootstrap iterations

RRs for active-duty HSI encounters at 10 CONUS U.S. Army installations per 1° increase in annual index of heat from 2-year block bootstrap negative binomial models with basic (empirical) confidence intervals based on 2,000 replicates, controlling for installation-level effects and long-term time trends. Temperature, HI, and WBGT categories reflect annual mean values in °F. Solid points reflect the mean of bootstrap estimates and non-filed points reflect the original sample (non-bootstrap) estimate. 

```{r}


full_year <-
  amb_boot_2yr_block %>% 
    unnest(tidy) %>%
    mutate(type = "Ambulatory") %>% 
    dplyr::select(-amb_data) %>% 
    bind_rows(
  hosp_boot_2yr_block %>% 
    unnest(tidy) %>%
    mutate(type = "Hospitalizations") %>% 
    dplyr::select(-hosp_data)
  ) %>% bind_rows(
  rme_boot_2yr_block %>% 
    unnest(tidy) %>%
    mutate(type = "Reportable Events") %>% 
    dplyr::select(-re_data)) %>% 
  filter(index %in% c("mean_tmp", "mean_hi","mean_wbgt")) %>% 
    mutate(avg_period = "Full year") %>% 
    dplyr::select(-boot) %>% 
    filter(term %in% "value") %>%
    mutate(index = fct_relevel(index, c("mean_wbgt", "mean_hi")),  # orders from bottom to top
           #index = forcats::fct_reorder(index, desc(statistic - bias )) # order index by bootstrap mean (statistic - bias) for plot appearance
           index = dplyr::recode(index,
                                `mean_tmp` = "Temperature (°F)",
                                `mean_hi` = "Heat Index (°F)",
                                `mean_wbgt` = "WBGT (°F)"))
  
heat_season <-
  amb_boot_2yr_block %>% 
    unnest(tidy) %>%
    mutate(type = "Ambulatory",
           avg_period = "May-Sep") %>% 
    dplyr::select(-amb_data) %>% 
  bind_rows(
    hosp_boot_2yr_block %>% 
    unnest(tidy) %>%
    mutate(type = "Hospitalizations",
           avg_period = "May-Sep") %>% 
    dplyr::select(-hosp_data)
  ) %>% bind_rows(
  rme_boot_2yr_block %>% 
    unnest(tidy) %>%
    mutate(type = "Reportable Events",
           avg_period = "May-Sep") %>% 
    dplyr::select(-re_data)
  ) %>%
  filter(index %in% c("mean_tmp_may_sep", "mean_hi_may_sep","mean_wbgt_may_sep")) %>% 
  dplyr::select(-boot) %>% 
    filter(term %in% "value") %>%
    mutate(index = fct_relevel(index, c("mean_wbgt", "mean_hi")),  # orders from bottom to top
           #index = forcats::fct_reorder(index, desc(statistic - bias )) # order index by bootstrap mean (statistic - bias) for plot appearance
           index = dplyr::recode(index,
                                `mean_tmp_may_sep` = "Temperature (°F)",
                                `mean_hi_may_sep` = "Heat Index (°F)",
                                `mean_wbgt_may_sep` = "WBGT (°F)")
                            ) 


full_year %>%
  bind_rows(heat_season) %>% 
  ggplot() +
        geom_point(aes(x = exp(statistic), y = index), shape = 1, fill = "white", color = "green4", size = 3.25) +
        geom_point(aes(x = exp(statistic - bias), y = index), size = 3.25) +
        geom_text(aes(x = exp(statistic - bias), y = index, 
                      label = round(exp(statistic - bias), 2)), 
                      hjust = 0.5, vjust = 2, size = 3) +
        geom_errorbarh(
          aes(y = index,
              xmin = exp(conf.low),
              xmax = exp(conf.high)), 
          size = 1.03, height = 0.2) +
         geom_vline(aes(xintercept = 1), colour = "blue", linetype = "dashed") +
         facet_grid(vars(avg_period), vars(type)) +
         theme_bw() +
         theme(#axis.text.y = element_text(size = rel(0.75)),
               axis.title.y = element_blank()) +
         xlab("Rate Ratio") +
#  ggtitle("Rate ratios for full-year and heat season indices of heat and HSI encounters\nat 10 CONUS U.S. Army installations") + 
#  labs(caption = "RRs per 1 degree increase in annual index of heat (mean of daily means) from 2-year block bootstrap negative binomial models\nwith basic (empirical) confidence intervals based on 10,000 replicates, controlling for installation-level effects.\nSolid points reflect the mean of bootstrap estimates and unfilled points reflect the original sample (non-bootstrap) estimate.") +
   theme(plot.caption = element_text(hjust = 0, size = 9)) 


# ggsave(filename = "figure2_rev.tiff", path = "output")


```


## Grouped IRRs
## IRRs of temperature-based indices


```{r}

joined_boot_2yr <-
  amb_boot_2yr_block %>% 
      unnest(tidy) %>%
      mutate(type = "Ambulatory") %>% 
      dplyr::select(-amb_data) %>% 
      bind_rows(
    hosp_boot_2yr_block %>% 
      unnest(tidy) %>%
      mutate(type = "Hospitalizations") %>% 
      dplyr::select(-hosp_data)
    ) %>% bind_rows(
    rme_boot_2yr_block %>% 
      unnest(tidy) %>%
      mutate(type = "Reportable Events") %>% 
      dplyr::select(-re_data)) %>% 
    filter(term %in% "value") %>% 
    dplyr::select(-c(boot, tidy_bca)) %>% 
  mutate(cat = case_when(str_detect(index, "hour")  ~ "Hours",
                         str_detect(index, "day")  ~ "Days",
                         str_detect(index, "anom")  ~ "Anomaly",
                         str_detect(index, "mean")  ~ "Mean",
                         str_detect(index, "max")  ~ "Maximum"),
         season = case_when(str_detect(index, "may")  ~ "Heat Season",
                            TRUE ~ "Full Year"),
         index_scale = case_when(str_detect(index, "tmp")  ~ "Temperature",
                                 str_detect(index, "hi")  ~ "Heat Index",
                                 str_detect(index, "wbgt")  ~ "WBGT"),
         index_name = dplyr::recode(index, mean_tmp = "Mean Tmp",
                          mean_hi = "Mean HI",
                          mean_wbgt = "Mean WBGT",
                          max_tmp = "Max Tmp",
                          max_hi = "Max HI",
                          max_wbgt = "Max WBGT",
                          mean_tmp_may_sep = "Mean Tmp HS",
                          mean_hi_may_sep = "Mean HI HS",
                          mean_wbgt_may_sep = "Mean WBGT HS",
                          max_tmp_may_sep = "Max Tmp HS",
                          max_hi_may_sep = "Max HI HS",
                          max_wbgt_may_sep = "Max WBGT HS",
                          hours_tmp_gt90 = "Hrs Tmp > 90",
                          hours_tmp_gt100 = "Hrs Tmp > 100",
                          hours_hi_gt90 = "Hrs HI > 90",
                          hours_hi_gt105 = "Hrs HI > 105",
                          hours_wbgt_gt85 = "Hrs WBGT > 85",
                          hours_wbgt_gt90 = "Hrs WBGT > 90",
                          tmp_anomaly = "Tmp Anomaly",
                          hi_anomaly = "HI Anomaly",
                          wbgt_anomaly = "WBGT Anomaly",
                          days_tmp_gt1sd = "Days Tmp > 1 SD",
                          days_hi_gt1sd = "Days HI > 1 SD",
                          days_wbgt_gt1sd = "Days WBGT > 1 SD",
                          tmp_anomaly_may_sep = "Tmp Anomaly HS",
                          hi_anomaly_may_sep = "HI Anomaly HS",
                          wbgt_anomaly_may_sep = "WBGT Anomaly HS",
                          days_tmp_gt1sd_may_sep = "Days Tmp > 1 SD HS",
                          days_hi_gt1sd_may_sep = "Days HI > 1 SD HS",
                          days_wbgt_gt1sd_may_sep = "Days WBGT > 1 SD HS"),
         index_scale = fct_relevel(index_scale, c("Temperature", "Heat Index", "WBGT")),
         season = fct_relevel(season, c( "Full Year", "Heat Season")),
         cat = fct_relevel(cat, c("Mean", "Maximum", "Anomaly", "Hours")))
                                 

joined_boot_2yr
# write_rds(joined_boot_2yr, file = "data/joined_boot_2yr.rds")

joined_boot_2yr <-
  read_rds(file = "data/joined_boot_2yr.rds")

```



```{r}


joined_boot_2yr %>% 
   ggplot() +
        geom_point(aes(x = exp(statistic), y = index_name), shape = 1, fill = "white", color = "green4", size = 3.25) +
        geom_point(aes(x = exp(statistic - bias), y = index_name), size = 3.25) +
        geom_text(aes(x = exp(statistic - bias), y = index_name, 
                      label = round(exp(statistic - bias), 2)), 
                      hjust = 0.5, vjust = 2, size = 3) +
        geom_errorbarh(
          aes(y = index_name,
              xmin = exp(conf.low),
              xmax = exp(conf.high)), 
          size = 1.03, height = 0.2) +
         geom_vline(aes(xintercept = 1), colour = "blue", linetype = "dashed") +
         facet_grid(cat + season ~ type, scales = "free", drop = TRUE) +
         theme_bw() +
         theme(#axis.text.y = element_text(size = rel(0.75)),
               axis.title.y = element_blank()) +
         xlab("Rate Ratio") +
   theme(plot.caption = element_text(hjust = 0, size = 9)) 



#  ggtitle("Rate ratios for full-year and heat season indices of heat and HSI encounters\nat 10 CONUS U.S. Army installations") + 
#  labs(caption = "RRs per 1 degree increase in annual index of heat (mean of daily means) from 2-year block bootstrap negative binomial models\nwith basic (empirical) confidence intervals based on 10,000 replicates, controlling for installation-level effects.\nSolid points reflect the mean of bootstrap estimates and unfilled points reflect the original sample (non-bootstrap) estimate.") +


```

### Hours (per 10 hour increment)
```{r}

joined_boot_2yr %>%
  filter(cat %in% "Hours") %>% 
   ggplot() +
        geom_point(aes(x = exp(statistic), y = index_name), shape = 1, fill = "white", color = "green4", size = 3.25) +
        geom_point(aes(x = exp(statistic - bias), y = index_name), size = 3.25) +
        geom_text(aes(x = exp(statistic - bias), y = index_name, 
                      label = round(exp(statistic - bias), 2)), 
                      hjust = 0.5, vjust = 2, size = 3) +
        geom_errorbarh(
          aes(y = index_name,
              xmin = exp(conf.low),
              xmax = exp(conf.high)), 
          size = 1.03, height = 0.2) +
         geom_vline(aes(xintercept = 1), colour = "blue", linetype = "dashed") +
         facet_grid(season + index_scale ~ type, scales = "free", drop = TRUE) +
         theme_bw() +
         theme(#axis.text.y = element_text(size = rel(0.75)),
               axis.title.y = element_blank()) +
         xlab("Rate Ratio") +
   theme(plot.caption = element_text(hjust = 0, size = 9)) 

# ggsave(filename = "hours_rr_rev.tiff", path = "output")

```


## Days

```{r}

joined_boot_2yr %>%
  filter(cat %in% "Days") %>% 
   mutate(index_name = fct_relevel(index_name, c("Days WBGT > 1 SD", "Days HI > 1 SD", "Days Tmp > 1 SD", 
                                                 "Days WBGT > 1 SD HS", "Days HI > 1 SD HS", "Days Tmp > 1 SD HS"))) %>% 
   ggplot() +
        geom_point(aes(x = exp(statistic), y = index_name), shape = 1, fill = "white", color = "green4", size = 3.25) +
        geom_point(aes(x = exp(statistic - bias), y = index_name), size = 3.25) +
        geom_text(aes(x = exp(statistic - bias), y = index_name, 
                      label = round(exp(statistic - bias), 2)), 
                      hjust = 0.5, vjust = 2, size = 3) +
        geom_errorbarh(
          aes(y = index_name,
              xmin = exp(conf.low),
              xmax = exp(conf.high)), 
          size = 1.03, height = 0.2) +
         geom_vline(aes(xintercept = 1), colour = "blue", linetype = "dashed") +
         facet_grid(season ~ type, scales = "free", drop = TRUE) +
         theme_bw() +
         theme(#axis.text.y = element_text(size = rel(0.75)),
               axis.title.y = element_blank()) +
         xlab("Rate Ratio") +
   theme(plot.caption = element_text(hjust = 0, size = 9))

# ggsave(filename = "days_rr_rev.tiff", path = "output")

```


### Degree Indices
```{r}

joined_boot_2yr %>%
  filter(cat %in% c("Mean", "Maximum", "Anomaly")) %>% 
   mutate(index_name = fct_relevel(index_name, c("WBGT Anomaly HS", "HI Anomaly HS", "Tmp Anomaly HS",
                                                 "WBGT Anomaly", "HI Anomaly", "Tmp Anomaly",
                                                 "Max WBGT HS", "Max HI HS", "Max Tmp HS",
                                                 "Max WBGT", "Max HI", "Max Tmp",
                                                 "Mean WBGT HS", "Mean HI HS", "Mean Tmp HS",
                                                 "Mean WBGT", "Mean HI", "Mean Tmp"))) %>% 
   ggplot() +
        geom_point(aes(x = exp(statistic), y = index_name), shape = 1, fill = "white", color = "green4", size = 3.25) +
        geom_point(aes(x = exp(statistic - bias), y = index_name), size = 3.25) +
        geom_text(aes(x = exp(statistic - bias), y = index_name, 
                      label = round(exp(statistic - bias), 2)), 
                      hjust = 0.5, vjust = 1.75, size = 2) +
        geom_errorbarh(
          aes(y = index_name,
              xmin = exp(conf.low),
              xmax = exp(conf.high)), 
          size = 1.03, height = 0.2) +
         geom_vline(aes(xintercept = 1), colour = "blue", linetype = "dashed") +
         facet_grid(season + cat ~ type, scales = "free", drop = TRUE) +
         theme_bw() +
         theme(#axis.text.y = element_text(size = rel(0.75)),
               axis.title.y = element_blank()) +
         xlab("Rate Ratio") +
   theme(plot.caption = element_text(hjust = 0, size = 9))

# ggsave(filename = "degrees_rr_rev.tiff", path = "output")
```


### Model Result Tables
```{r}

boot2_table <-
  joined_boot_2yr %>%
    mutate(rr = exp(statistic),
           rr_low = exp(conf.low),
           rr_high = exp(conf.high),
           rate_ratio = paste0(round(rr, 3), " (", round(rr_low, 3), ", ", round(rr_high, 3), ")")) %>% 
    dplyr::select(index_name, type, cat, season, index_scale, rate_ratio) %>% 
    pivot_wider(names_from = type, values_from = rate_ratio) %>% 
    arrange(cat)

boot2_table

boot2_table %>% as.data.frame()

#clipr::write_clip(boot2_table)

```






# Sensitivity analysis plots

```{r}

a1 <-
amb_boot_2yr_block %>% 
    unnest(tidy) %>%
        filter(term %in% "value") %>%
    mutate(index = fct_reorder(index, exp(statistic))) %>% 
   ggplot() +
        geom_point(aes(x = exp(statistic), y = index)) +
        geom_errorbarh(
          aes(y = index,
              xmin = exp(conf.low),
              xmax = exp(conf.high))) +
         geom_vline(aes(xintercept = 1), colour = "blue") +
         coord_cartesian(xlim = c(0.75, 2.0)) +
         theme_bw() +
         theme(axis.text.y = element_text(size = rel(0.75)),
               axis.title.y = element_blank()) +
         ggtitle("Ambulatory \n 2 year block") +
         xlab("Rate Ratio") +
         theme(plot.title = element_text(size = 8))

a2 <-
amb_boot_2yr_block %>% 
    unnest(tidy_bca) %>%
        filter(term %in% "value") %>%
    mutate(index = fct_reorder(index, exp(statistic))) %>% 
   ggplot() +
        geom_point(aes(x = exp(statistic), y = index)) +
        geom_errorbarh(
          aes(y = index,
              xmin = exp(conf.low),
              xmax = exp(conf.high))) +
         geom_vline(aes(xintercept = 1), colour = "blue") +
         coord_cartesian(xlim = c(0.75, 2.0)) +
         theme_bw() +
         theme(axis.text.y = element_text(size = rel(0.75)),
               axis.title.y = element_blank()) +
         ggtitle("Ambulatory \n 2 year block - Bca CIs") +
         xlab("Rate Ratio") +
         theme(plot.title = element_text(size = 8))

a3 <-
amb_boot_3yr_block %>% 
    unnest(tidy) %>%
        filter(term %in% "value") %>%
    mutate(index = fct_reorder(index, exp(statistic))) %>% 
   ggplot() +
        geom_point(aes(x = exp(statistic), y = index)) +
        geom_errorbarh(
          aes(y = index,
              xmin = exp(conf.low),
              xmax = exp(conf.high))) +
         geom_vline(aes(xintercept = 1), colour = "blue") +
         coord_cartesian(xlim = c(0.75, 2.0)) +
         theme_bw() +
         theme(axis.text.y = element_text(size = rel(0.75)),
               axis.title.y = element_blank()) +
         ggtitle("Ambulatory \n 3 year block") +
         xlab("Rate Ratio") +
         theme(plot.title = element_text(size = 8))


a4 <-
amb_boot_std %>% 
    unnest(tidy) %>%
        filter(term %in% "value") %>%
    mutate(index = fct_reorder(index, exp(statistic))) %>% 
   ggplot() +
        geom_point(aes(x = exp(statistic), y = index)) +
        geom_errorbarh(
          aes(y = index,
              xmin = exp(conf.low),
              xmax = exp(conf.high))) +
         geom_vline(aes(xintercept = 1), colour = "blue") +
         coord_cartesian(xlim = c(0.75, 2.0)) +
         theme_bw() +
         theme(axis.text.y = element_text(size = rel(0.75)),
               axis.title.y = element_blank()) +
         ggtitle("Ambulatory \n standard bootstrap") +
         xlab("Rate Ratio") +
         theme(plot.title = element_text(size = 8))

a5 <-
amb_nb %>% 
    unnest(nb_tidy) %>%
        filter(term %in% "value") %>%
    mutate(index = fct_reorder(index, exp(estimate))) %>% 
   ggplot() +
        geom_point(aes(x = exp(estimate), y = index)) +
        geom_errorbarh(
          aes(y = index,
              xmin = exp(conf.low),
              xmax = exp(conf.high))) +
         geom_vline(aes(xintercept = 1), colour = "blue") +
         coord_cartesian(xlim = c(0.75, 2.0)) +
         theme_bw() +
         theme(axis.text.y = element_text(size = rel(0.75)),
               axis.title.y = element_blank()) +
         ggtitle("Ambulatory \n neg bin - no year term, no bootstrap") +
         xlab("Rate Ratio") +
         theme(plot.title = element_text(size = 8))

a6 <-
amb_nb %>% 
    unnest(nb_year_tidy) %>%
        filter(term %in% "value") %>%
    mutate(index = fct_reorder(index, exp(estimate))) %>% 
   ggplot() +
        geom_point(aes(x = exp(estimate), y = index)) +
        geom_errorbarh(
          aes(y = index,
              xmin = exp(conf.low),
              xmax = exp(conf.high))) +
         geom_vline(aes(xintercept = 1), colour = "blue") +
         coord_cartesian(xlim = c(0.75, 2.0)) +
         theme_bw() +
         theme(axis.text.y = element_text(size = rel(0.75)),
               axis.title.y = element_blank()) +
         ggtitle("Ambulatory \n neg bin - with year term, no bootstrap") +
         xlab("Rate Ratio") +
         theme(plot.title = element_text(size = 8))


#patchwork
(a1 + a2 + a3) / (a4 + a5 + a6)

#ggsave("output/amb_sensitivity.tiff", width = 10, height = 6)
```



```{r}

r1 <-
rme_boot_2yr_block %>% 
    unnest(tidy) %>%
        filter(term %in% "value") %>%
    mutate(index = fct_reorder(index, exp(statistic))) %>% 
   ggplot() +
        geom_point(aes(x = exp(statistic), y = index)) +
        geom_errorbarh(
          aes(y = index,
              xmin = exp(conf.low),
              xmax = exp(conf.high))) +
         geom_vline(aes(xintercept = 1), colour = "blue") +
         coord_cartesian(xlim = c(0.75, 2.0)) +
         theme_bw() +
         theme(axis.text.y = element_text(size = rel(0.75)),
               axis.title.y = element_blank()) +
         ggtitle("Reportable Events \n 2 year block") +
         xlab("Rate Ratio") +
         theme(plot.title = element_text(size = 8))

r2 <-
rme_boot_2yr_block %>% 
    unnest(tidy_bca) %>%
        filter(term %in% "value") %>%
    mutate(index = fct_reorder(index, exp(statistic))) %>% 
   ggplot() +
        geom_point(aes(x = exp(statistic), y = index)) +
        geom_errorbarh(
          aes(y = index,
              xmin = exp(conf.low),
              xmax = exp(conf.high))) +
         geom_vline(aes(xintercept = 1), colour = "blue") +
         coord_cartesian(xlim = c(0.75, 2.0)) +
         theme_bw() +
         theme(axis.text.y = element_text(size = rel(0.75)),
               axis.title.y = element_blank()) +
         ggtitle("Reportable Events \n 2 year block - Bca CIs") +
         xlab("Rate Ratio") +
         theme(plot.title = element_text(size = 8))

r3 <-
rme_boot_3yr_block %>% 
    unnest(tidy) %>%
        filter(term %in% "value") %>%
    mutate(index = fct_reorder(index, exp(statistic))) %>% 
   ggplot() +
        geom_point(aes(x = exp(statistic), y = index)) +
        geom_errorbarh(
          aes(y = index,
              xmin = exp(conf.low),
              xmax = exp(conf.high))) +
         geom_vline(aes(xintercept = 1), colour = "blue") +
         coord_cartesian(xlim = c(0.75, 2.0)) +
         theme_bw() +
         theme(axis.text.y = element_text(size = rel(0.75)),
               axis.title.y = element_blank()) +
         ggtitle("Reportable Events \n 3 year block") +
         xlab("Rate Ratio") +
         theme(plot.title = element_text(size = 8))


r4 <-
rme_boot_std %>% 
    unnest(tidy) %>%
        filter(term %in% "value") %>%
    mutate(index = fct_reorder(index, exp(statistic))) %>% 
   ggplot() +
        geom_point(aes(x = exp(statistic), y = index)) +
        geom_errorbarh(
          aes(y = index,
              xmin = exp(conf.low),
              xmax = exp(conf.high))) +
         geom_vline(aes(xintercept = 1), colour = "blue") +
         coord_cartesian(xlim = c(0.75, 2.0)) +
         theme_bw() +
         theme(axis.text.y = element_text(size = rel(0.75)),
               axis.title.y = element_blank()) +
         ggtitle("Reportable Events \n standard bootstrap") +
         xlab("Rate Ratio") +
         theme(plot.title = element_text(size = 8))

r5 <-
rme_nb %>% 
    unnest(nb_tidy) %>%
        filter(term %in% "value") %>%
    mutate(index = fct_reorder(index, exp(estimate))) %>% 
   ggplot() +
        geom_point(aes(x = exp(estimate), y = index)) +
        geom_errorbarh(
          aes(y = index,
              xmin = exp(conf.low),
              xmax = exp(conf.high))) +
         geom_vline(aes(xintercept = 1), colour = "blue") +
         coord_cartesian(xlim = c(0.75, 2.0)) +
         theme_bw() +
         theme(axis.text.y = element_text(size = rel(0.75)),
               axis.title.y = element_blank()) +
         ggtitle("Reportable Events \n neg bin - no year term, no bootstrap") +
         xlab("Rate Ratio") +
         theme(plot.title = element_text(size = 8))

r6 <-
rme_nb %>% 
    unnest(nb_year_tidy) %>%
        filter(term %in% "value") %>%
    mutate(index = fct_reorder(index, exp(estimate))) %>% 
   ggplot() +
        geom_point(aes(x = exp(estimate), y = index)) +
        geom_errorbarh(
          aes(y = index,
              xmin = exp(conf.low),
              xmax = exp(conf.high))) +
         geom_vline(aes(xintercept = 1), colour = "blue") +
         coord_cartesian(xlim = c(0.75, 2.0)) +
         theme_bw() +
         theme(axis.text.y = element_text(size = rel(0.75)),
               axis.title.y = element_blank()) +
         ggtitle("Reportable Events \n neg bin - with year term, no bootstrap") +
         xlab("Rate Ratio") +
         theme(plot.title = element_text(size = 8))


#patchwork
(r1 + r2 + r3) / (r4 + r5 + r6)

# ggsave("output/rme_sensitivity.tiff", width = 10, height = 6)
```


Hospitalization sensitivity
```{r}

h1 <-
hosp_boot_2yr_block %>% 
    unnest(tidy) %>%
        filter(term %in% "value") %>%
    mutate(index = fct_reorder(index, exp(statistic))) %>% 
   ggplot() +
        geom_point(aes(x = exp(statistic), y = index)) +
        geom_errorbarh(
          aes(y = index,
              xmin = exp(conf.low),
              xmax = exp(conf.high))) +
         geom_vline(aes(xintercept = 1), colour = "blue") +
         coord_cartesian(xlim = c(0.75, 2.0)) +
         theme_bw() +
         theme(axis.text.y = element_text(size = rel(0.75)),
               axis.title.y = element_blank()) +
         ggtitle("Hospitalizations \n 2 year block") +
         xlab("Rate Ratio") +
         theme(plot.title = element_text(size = 8))

# (h2): No bca models for hospitalization

h3 <-
hosp_boot_3yr_block %>% 
    unnest(tidy) %>%
        filter(term %in% "value") %>%
    mutate(index = fct_reorder(index, exp(statistic))) %>% 
   ggplot() +
        geom_point(aes(x = exp(statistic), y = index)) +
        geom_errorbarh(
          aes(y = index,
              xmin = exp(conf.low),
              xmax = exp(conf.high))) +
         geom_vline(aes(xintercept = 1), colour = "blue") +
         coord_cartesian(xlim = c(0.75, 2.0)) +
         theme_bw() +
         theme(axis.text.y = element_text(size = rel(0.75)),
               axis.title.y = element_blank()) +
         ggtitle("Hospitalizations \n 3 year block") +
         xlab("Rate Ratio") +
         theme(plot.title = element_text(size = 8))


h4 <-
hosp_boot_std %>% 
    unnest(tidy) %>%
        filter(term %in% "value") %>%
    mutate(index = fct_reorder(index, exp(statistic))) %>% 
   ggplot() +
        geom_point(aes(x = exp(statistic), y = index)) +
        geom_errorbarh(
          aes(y = index,
              xmin = exp(conf.low),
              xmax = exp(conf.high))) +
         geom_vline(aes(xintercept = 1), colour = "blue") +
         coord_cartesian(xlim = c(0.75, 2.0)) +
         theme_bw() +
         theme(axis.text.y = element_text(size = rel(0.75)),
               axis.title.y = element_blank()) +
         ggtitle("Hospitalizations \n standard bootstrap") +
         xlab("Rate Ratio") +
         theme(plot.title = element_text(size = 8))

h5 <-
hosp_nb %>% 
    unnest(nb_tidy) %>%
        filter(term %in% "value") %>%
    mutate(index = fct_reorder(index, exp(estimate))) %>% 
   ggplot() +
        geom_point(aes(x = exp(estimate), y = index)) +
        geom_errorbarh(
          aes(y = index,
              xmin = exp(conf.low),
              xmax = exp(conf.high))) +
         geom_vline(aes(xintercept = 1), colour = "blue") +
         coord_cartesian(xlim = c(0.75, 2.0)) +
         theme_bw() +
         theme(axis.text.y = element_text(size = rel(0.75)),
               axis.title.y = element_blank()) +
         ggtitle("Hospitalizations \n neg bin - no year term, no bootstrap") +
         xlab("Rate Ratio") +
         theme(plot.title = element_text(size = 8))

h6 <-
hosp_nb %>% 
    unnest(nb_year_tidy) %>%
        filter(term %in% "value") %>%
    mutate(index = fct_reorder(index, exp(estimate))) %>% 
   ggplot() +
        geom_point(aes(x = exp(estimate), y = index)) +
        geom_errorbarh(
          aes(y = index,
              xmin = exp(conf.low),
              xmax = exp(conf.high))) +
         geom_vline(aes(xintercept = 1), colour = "blue") +
         coord_cartesian(xlim = c(0.75, 2.0)) +
         theme_bw() +
         theme(axis.text.y = element_text(size = rel(0.75)),
               axis.title.y = element_blank()) +
         ggtitle("Hospitalizations \n neg bin - with year term, no bootstrap") +
         xlab("Rate Ratio") +
         theme(plot.title = element_text(size = 8))


#patchwork
(h1  + h3) / (h4 + h5 + h6)

# ggsave("output/hosp_sensitivity.tiff", width = 10, height = 6)
```



## Model Statistics

```{r}


# Negative binomial, no year
amb_nb %>% 
  mutate(nb_glance =  map(nb_mod, broom::glance)) %>% 
  unnest(nb_glance) %>% 
  dplyr::select(-c("data", "nb_mod", "nb_tidy", "nb_year_mod", "nb_year_tidy"))

                   
# Negative binomial, year
amb_nb %>% 
  mutate(nb_glance =  map(nb_year_mod, broom::glance)) %>% 
  unnest(nb_glance) %>% 
  dplyr::select(-c("data", "nb_mod", "nb_tidy", "nb_year_mod", "nb_year_tidy"))



# Negative binomial, no year
hosp_nb %>%
  slice_head(n = 6) %>% 
  mutate(nb_glance =  map(nb_mod, broom::glance)) %>% 
  unnest(nb_glance) %>% 
  dplyr::select(-c("data", "nb_mod", "nb_tidy", "nb_year_mod", "nb_year_tidy"))

                   
# Negative binomial, year
hosp_nb %>%
  slice_head(n = 6) %>% 
  mutate(nb_glance =  map(nb_year_mod, broom::glance)) %>% 
  unnest(nb_glance) %>% 
  dplyr::select(-c("data", "nb_mod", "nb_tidy", "nb_year_mod", "nb_year_tidy"))



# Negative binomial, no year
rme_nb %>% 
  mutate(nb_glance =  map(nb_mod, broom::glance)) %>% 
  unnest(nb_glance) %>% 
  dplyr::select(-c("data", "nb_mod", "nb_tidy", "nb_year_mod", "nb_year_tidy"))

                   
# Negative binomial, year
rme_nb %>% 
  mutate(nb_glance =  map(nb_year_mod, broom::glance)) %>% 
  unnest(nb_glance) %>% 
  dplyr::select(-c("data", "nb_mod", "nb_tidy", "nb_year_mod", "nb_year_tidy"))

```


